---
title: "Visualizing Super Tuesday and Beyond"
author: "Devraj Kori"
date: "3/4/2020"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(tidycensus)
library(rvest)    
library(gridExtra)
library(scales)
library(leaflet)
library(sf)
```

```{r other_functions,include=FALSE,echo=FALSE,warning=FALSE,message=FALSE}
rgb_max<-function(red,blue,green){
  rgb(red,blue,green,maxColorValue=255)
}

```

```{r read_538_data,include=FALSE}
#read in primary poll averages
primary_averages<-read_csv("538_polls/pres_primary_avgs_2020.csv")

#read in total polls
primary_polls<-read_csv("538_polls/president_primary_polls.csv")

```


```{r state_abbr,include=FALSE}
state_abbrevs<-read_csv(url("https://github.com/jasonong/List-of-US-States/raw/master/states.csv"))%>%
  rename(state=State)

```

```{r retrieve_super_tuesday_pop_votes,include=FALSE}
pop_vote_url<-"https://www.politico.com/2020-election/results/super-tuesday/"

pop_vote<-pop_vote_url%>%
  read_html()%>%
  html_nodes(css='#__next > div.jsx-3281836393.SuperTuesdayTable > div.jsx-3281836393.inner-container > table')%>%
  html_table(fill=TRUE)

pop_vote2<-pop_vote[[1]]
names(pop_vote2)<-pop_vote2[1,]
#give the first column a name or it'll get mad
names(pop_vote2)[1]<-"state_bad"
#going to hardcode the following transformations and hope politico doesn't change anything
pop_vote3<-pop_vote2%>%
  #remove rows that didn't read in correctly
  slice(3:16)%>%
  #manually specify state names
  mutate(state=c("Alabama","Virginia","North Carolina","Tennessee","Arkansas",
                 "Oklahoma","Minnesota","Texas","Maine","Massachusetts",
                 "Vermont","Colorado","Utah","California"))%>%
  #recreate delegate counts here
  mutate(delegate_count=as.numeric(gsub("[A-z]|\\.|([0-9]+%)","",state_bad)))%>%
  #remove bad state
  select(-state_bad)

```

```{r retrieve_census_geometries,include=FALSE}
#pull in state geometries from tidycensus
state_geometries<-get_acs(year=2018,variables=c("total_pop" = "B01001_001"),geography="state",
                    geometry=TRUE)%>%
  rename("state"=NAME)%>%
  #just keep state
  select(state)

```

```{r retrieve_wiki_table,include=FALSE}
#grab delegate counts from each state
wiki_url<-"https://en.wikipedia.org/w/index.php?title=2020_Democratic_Party_presidential_primaries&diff=943986491&oldid=943986233"

delegate_table<-wiki_url%>%
  read_html()%>%
  html_nodes(css='#mw-content-text > div.mw-parser-output > table:nth-child(128)')%>%
  html_table(fill=TRUE)
delegate_table2<-delegate_table[[1]]

#change names of delegate_table2
names(delegate_table2)<-c("Date","Day Delegates", "State Pledged", "Contest",
                          "Biden", "Bloomberg", "Buttigieg", "Gabbard", "Klobuchar",
                          "Sanders", "Warren")


#calculate pledged delegates per state
pledged_per_state<-delegate_table2%>%
  select(`State Pledged`, `Contest`)%>%
  #create state by removing primary stuff
  mutate(state=gsub(" \\(.*?\\)","",Contest))%>%
  mutate(state=gsub(" party-run","",state))%>%
  mutate(state=gsub(" firehouse","",state))%>%
  mutate(state=gsub(" [A-z]*$","",state))



```
[github repo](https://github.com/dkori/visualize-super-tuesday)

## What actually happened on Super Tuesday? 

I've noticed that the press coverage of Super Tuesday of the 2020 Democratic primary seemed to focus almost exclusively on who "won" specific states. This is a familiar format of election coverage for most of us as its how we generally hear national results for general elections. 

In the general election for president, almost every state is winner-take-all, meaning whoever receives a plurality of the vote in that state claims all of the electors from that state. Unlike the general election, in the Democratic primary, almost every state divides up its "delegates" sort of proportionally among all of the candidates who hit a certain threshold.

That means that presenting election results in terms of state wins can be misleading for a couple reasons: 
1. It treats states where a single candidate gets all of the delegates, and states where delegates are equally split between two or more candidates exactly the same. 
2. Because most of us don't know the relative populations of all 50 states off the top of our heads, it makes it hard to compare candidate A's strongest performing states with Candidate B's. 

```{r compare_wins_to_delegates,echo=FALSE,warning=FALSE,message=FALSE}
#calculate wins per candidate
win_counter<-delegate_table2%>%
  #remove total
  filter(Contest!="Total")%>%
  #create state by removing primary stuff
  mutate(state=gsub(" \\(.*?\\)","",Contest))%>%
  mutate(state=gsub(" party-run","",state))%>%
  mutate(state=gsub(" firehouse","",state))%>%
  mutate(state=gsub(" [A-z]*$","",state))%>%
  rowwise()%>%
  #create a max delegates column
  mutate(max_delegates=max(Biden,Buttigieg,Sanders,Bloomberg,na.rm=TRUE))%>%
  ungroup()%>%
  #create win binaries per candidate
  mutate(Buttigieg_win=(Buttigieg==max_delegates),
         Sanders_win=(Sanders==max_delegates),
         Biden_win=(Biden==max_delegates),
         Bloomberg_win=(Bloomberg==max_delegates))
#create a frame indicating wins per candidate
win_frame<-data.frame(Buttigieg=sum(win_counter$Buttigieg_win,na.rm=TRUE),
                      Sanders=sum(win_counter$Sanders_win,na.rm=TRUE),
                      Biden=sum(win_counter$Biden_win,na.rm=TRUE),
                      Bloomberg=sum(win_counter$Bloomberg_win,na.rm=TRUE),
                      Warren=0,
                      Klobuchar=0,
                      Gabbard=0)%>%
  gather()%>%
  mutate(x="wins")
#create a frame indicating delegates won per candidate
delegate_frame<-data.frame(Buttigieg=sum(win_counter$Buttigieg,na.rm=TRUE),
                      Sanders=sum(win_counter$Sanders,na.rm=TRUE),
                      Biden=sum(win_counter$Biden,na.rm=TRUE),
                      Bloomberg=sum(win_counter$Bloomberg,na.rm=TRUE),
                      Warren=sum(win_counter$Warren,na.rm=TRUE),
                      Klobuchar=sum(win_counter$Klobuchar,na.rm=TRUE),
                      Gabbard=sum(win_counter$Gabbard,na.rm=TRUE))%>%
  gather()%>%
  mutate(x="delegates")

#plot results
rbind(delegate_frame,win_frame)%>%
  ggplot(aes(x=x,y=value,fill=key))+
  geom_bar(stat="identity",position="fill",width=.4)+
  scale_y_continuous(label=percent)+
  theme(legend.position="bottom")+
  labs(x="",y="percent",fill="",title="Democratic Primary (as of 4 March 2020)")+
  scale_fill_brewer(palette="Accent")

```

The column on the left more accurately depicts where each candidate stands, while the chart on the right shows the stat underlying most election coverage. 

Last night, you probably saw a map that looked similar to this on your preferred election coverage site.

```{r state_winners, echo=FALSE,warning=FALSE,message=FALSE}


super_tuesday_wins<-win_counter%>%
  filter(grepl("Tuesday",Date))%>%
  #remove American Samoa (sorry guys)
  filter(!grepl("Samoa",state))%>%
  #create a column indicating if Sanders or Biden won
  mutate(winner=ifelse(Sanders_win,"Sanders","Biden"))%>%
  #merge in state geometries
  left_join(state_geometries)
#create palette for chart
pal <- colorFactor(
  palette = "viridis",
  domain = super_tuesday_wins$winner,
  reverse=TRUE)
leaflet()%>%
  addPolygons(data=st_as_sf(super_tuesday_wins),
              stroke=FALSE,
              fillOpacity=1,
              color=~pal(winner))%>%
  addLegend(data=st_as_sf(super_tuesday_wins),
    position="bottomright",
    pal=pal,
    values=~winner,
    labels=~winner,
    opacity=1)


```

When really, something like this better shows the intensity of victories in each state. 
```{r state_delegate, echo=FALSE,warning=FALSE,message=FALSE}
super_tuesday_delegates<-win_counter%>%
  filter(grepl("Tuesday",Date))%>%
  #remove American Samoa (sorry guys)
  filter(!grepl("Samoa",state))%>%
  #limit to just state, biden, and sanders
  select(state,Sanders,Biden)%>%
  #replace NAs with 0s (just in case)
  replace_na(list(Sanders=0,Biden=0))%>%
  #calculate sanders share
  mutate(biden_margin=Biden-Sanders)%>%
  #merge in state geometries
  left_join(state_geometries)
#create palette for chart
pal <- colorNumeric(
  palette = "viridis",
  domain = super_tuesday_delegates$biden_margin,
  reverse = TRUE)
leaflet()%>%
  addPolygons(data=st_as_sf(super_tuesday_delegates),
              stroke=FALSE,
              fillOpacity=1,
              color=~pal(biden_margin))%>%
  addLegend(data=st_as_sf(super_tuesday_delegates),
    position="bottomright",
    pal=pal,
    values=~biden_margin,
    opacity=1,
    title="Biden delegate<br>margin",
    bins=5)

```


```{r state_delegates resized, echo=FALSE}
# super_tuesday_scaled<-win_counter%>%
#   filter(grepl("Tuesday",Date))%>%
#   #remove American Samoa (sorry guys)
#   filter(!grepl("Samoa",state))%>%
#   #replace NAs with 0s (just in case)
#   replace_na(list(Sanders=0,Biden=0))%>%
#   #calculate sanders share
#   mutate(sanders_share=Sanders/(Sanders+Biden))%>%
#   #merge in state geometries
#   left_join(state_geometries)%>%
#   st_as_sf()
# #create a vector of scaling factors
# scaling_factors<-as.numeric(super_tuesday_scaled$`State Pledged`)
# #make an sf object version
# sf_scaled<-st_geometry(super_tuesday_scaled)*scaling_factors
# #replace geometries
# super_tuesday_scaled2<-st_set_geometry(super_tuesday_scaled,sf_scaled)
# leaflet()%>%
#   addPolygons(data=st_as_sf(super_tuesday_scaled2),
#               stroke=FALSE,
#               fillOpacity=1,
#               color=~pal(sanders_share))
#%>%
  # addLegend(
  #   position="bottomright",
  #   pal=pal,
  #   values=~sanders_share,
  #   opacity=1,
  #   title="Sanders:Biden<br>Delegate Ratio")
```


This doesn't contradict the high-level narrative that Biden had a great night, but it paints a much more accurate picture of exactly how that great night went down.


## Are these results surprising? 

The big twist in the days leading up to Super Tuesday was two major candidates, Amy Klobuchar and Pete Buttigieg, both dropping out and endorsing Joe Biden. The results seemed to show that, perhaps unsurprisingly, Biden drastically outperformed the [lead-up polling](https://fivethirtyeight.com/features/what-makes-our-new-2020-democratic-primary-polling-averages-different/). 

```{r compare_polling_actual_biden,echo=FALSE,warning=FALSE,message=FALSE}
#create a function that takes a candidate's name and returns a two-column dataframe of state and that candidate's polling average
candidate_polling<-function(name){
  #start with primary averages
  temp_frame<-primary_averages%>%
    #limit to candidate
    filter(grepl(name,candidate_name))%>%
    #limit to just latest occurence of state
    slice(match(unique(primary_averages$state),state))%>%
    select(state,pct_estimate)
  #rename column for candidate
  names(temp_frame)[2]<-name
  #return temp_frame
  temp_frame
}
#create list of candidates to apply function over
candidates<-c("Sanders","Biden","Buttigieg","Klobuchar", "Warren")

#apply the function over all candidates, and join together
polling_by_candidate<-Reduce(full_join,
                              lapply(candidates,
                                     candidate_polling))%>%
  #replace klobuchar NA's with 0s
  replace_na(list(Klobuchar=0))

#compare Biden's actual popular vote to his polling averages by state
biden_comparison<-pop_vote3%>%
  select(state,Biden,delegate_count)%>%
  #make Biden's delegate count numeric
  mutate(Biden=as.numeric(gsub("%","",Biden)))%>%
  rename("Actual" = Biden)%>%
  left_join(polling_by_candidate%>%
              select(state,Biden)%>%
              rename("Projected" = Biden))%>%
  #create a column for the difference between projected and actual
  mutate(difference=Actual-Projected)%>%
  #merge in state abbreviations
  left_join(state_abbrevs)%>%
  ggplot(aes(x=Projected,y=Actual,color=difference,label=Abbreviation))+
  geom_point(aes(size=delegate_count),alpha=.7)+
  geom_text(nudge_x=2)+
  scale_color_viridis_c(limits=c(-10,25),
                        option="magma")+
  labs(title="Biden: projected vs actual vote share",
       y="Actual Vote %",
       x="Projected Vote%",
       color="Poll\nOutperformance",
       size="Delegates")+
  #scale_size_continuous(guide="none")+
  #add an equality line
  geom_abline(slope=1,intercept=0)+
  scale_x_continuous(limits=c(0,63))+
  scale_y_continuous(limits=c(0,63))

biden_comparison
```

Assuming the polling wasn't systematically wrong, this was probably due to a combination of Pete and Amy supporters voting for Biden because of their endorsements, and undecided voters choosing him as the standardbearer for the moderate wing of the party. 

But what about Sanders? To the extent that only one candidate can get the nomination, Joe's good night is Bernie's bad night. But in terms of his actual share of the vote, Bernie **met or outperformed his polling average (as calculated by 538) in every state.**

```{r compare_polling_actual_sanders,echo=FALSE,warning=FALSE,message=FALSE}
#compare Sanders's actual popular vote to his polling averages by state
sanders_comparison<-pop_vote3%>%
  select(state,Sanders,delegate_count)%>%
  #make Sanders's delegate count numeric
  mutate(Sanders=as.numeric(gsub("%","",Sanders)))%>%
  rename("Actual" = Sanders)%>%
  left_join(polling_by_candidate%>%
              select(state,Sanders)%>%
              rename("Projected" = Sanders))%>%
  #create a column for the difference between projected and actual
  mutate(difference=Actual-Projected)%>%
  #merge in state abbreviations
  left_join(state_abbrevs)%>%
  ggplot(aes(x=Projected,y=Actual,color=difference,label=Abbreviation))+
  geom_point(aes(size=delegate_count),alpha=.7)+
  geom_text(nudge_x=2)+
  scale_color_viridis_c(limits=c(-10,25),
                        option="magma")+
  labs(title="Sanders: projected vs actual vote share",
       y="Actual Vote %",
       x="Projected Vote%",
       color="Poll\nOutperformance",
       size="Delegates")+
  #scale_size_continuous(guide="none")+
  #add an equality line
  geom_abline(slope=1,intercept=0)+
  scale_x_continuous(limits=c(0,63))+
  scale_y_continuous(limits=c(0,63))

sanders_comparison

```


That's not to say that Sanders did *well*, just that he got about as many votes as the previous polling averages forecasted. The better question, then, is why did we expect him to do well?

This has at least a little to do with the overemphasis on "winning" states. Sanders was projected to win many Super Tuesday states, but was never really polling all that high in any of them, just high enough to keep his head above the rest of the pack. What seemed like a favorable position depended heavily on the moderate vote being split between several candidates. When candidates dropped out and their share mostly redistributed between those who remained, that lead shrunk. 

It's hard to say what the impact was of the coverage that inflated our expectations for Sanders. One the one hand, positive polling probably helped Sanders build enthusiasm and belief within his base. However, the abrupt shift away from that positivity may do more harm than good as he works to continue mobilizing supporters.

## What might happen next?

If current polling averages are to be trusted (more on that later), Sanders' path forward doesn't look promising. Biden is polling ahead of him, both in terms of states and possible delegates, in most of the contests for which we have polling information. 

The chart below compares polling averages for Biden and Sanders in upcoming contests. Note that this chart does not account for Klobuchar and Buttigieg supporters shifting to either candidate, as they overwhelmingly appear to have done for Biden on Tuesday. The actual reality, as things currently stand, is even bleaker for Sanders. 


```{r show_sanders_biden_polling_in_remaining,echo=FALSE,warning=FALSE,message=FALSE}


sanders_biden_comparison<-polling_by_candidate%>%
  #join in pledged
  inner_join(pledged_per_state%>%
               #limit to just after super tuesday
               slice(20:nrow(pledged_per_state)))%>%
  #make pledged per state numeric
  mutate(`State Pledged`=as.numeric(`State Pledged`))%>%
  #limit only to states where Biden's polling at at least .1% (excludes wyoming)
  filter(Biden>=.1)%>%
  #create a column for Sanders/Biden ratio
  mutate(`Sanders/Biden Ratio`=Sanders/Biden)%>%
  #merge in state abbreviations
  left_join(state_abbrevs)%>%
  #plot
  ggplot(aes(x=Biden,y=Sanders,color=`Sanders/Biden Ratio`,label=Abbreviation))+
  geom_point(aes(size=`State Pledged`),alpha=.7)+
  geom_text(nudge_x=2)+
  scale_color_viridis_c(limits=c(0,2.5))+
  labs(title="Sanders vs Biden projections in remaining contests\n(polls from before Pete and Amy dropped)",
       y="Sanders projected share",
       x="Biden projected share",
       color="Sanders:Biden\nratio",
       size="Pledged\ndelegates")+
  #scale_size_continuous(guide="none")+
  #add an equality line
  geom_abline(slope=1,intercept=0)+
  scale_x_continuous(limits=c(11,54))+
  scale_y_continuous(limits=c(11,54))

sanders_biden_comparison


```

(Source: 538 Polling Averages. Excludes the following contests where polling was unavailable: 
LA, KY, PR, KS, NE, WV, RI, HI, ID, DC, SD, AK, ND, DA, GU, VI, MP.)

There is of course still another candidate in the race. Since Sanders looks pretty far out, lets look at one extreme scenario that some think could help him regain a footing. 

```{r sanders_and_warren_biden_comparison,echo=FALSE,warning=FALSE,message=FALSE}
with_absorbed<-polling_by_candidate%>%
  #join in pledged
  inner_join(pledged_per_state%>%
               #limit to just after super tuesday
               slice(20:nrow(pledged_per_state)))%>%
  #make pledged per state numeric
  mutate(`State Pledged`=as.numeric(`State Pledged`))%>%
  #limit only to states where Biden's polling at at least .1% (excludes wyoming)
  filter(Biden>=.1)%>%
  #create a column for sanders warren combined
  mutate(sanders_plus_warren=Sanders+Warren)%>%
  #create a column for Biden, Amy, Pete combined
  mutate(biden_plus=Biden+Klobuchar+Buttigieg)%>%
  #create a column for Sanders/Biden ratio
  mutate(`Sanders/Biden Ratio`=sanders_plus_warren/biden_plus)%>%
  #merge in state abbreviations
  left_join(state_abbrevs)%>%
  #plot
  ggplot(aes(x=biden_plus,y=sanders_plus_warren,color=`Sanders/Biden Ratio`,label=Abbreviation))+
  geom_point(aes(size=`State Pledged`),alpha=.7)+
  geom_text(nudge_x=2)+
  scale_color_viridis_c(limits=c(0,2.5))+
  labs(title="Sanders vs Biden projections with perfect realignment\n(assuming Sanders absorbs Warren, Biden absorbs Amy/Pete)",
       y="Sanders + Warren combined projected share",
       x="Biden + Amy + Pete combined projected share",
       color="Sanders+:Biden+\nRatio\n",
       size="Pledged\ndelegates")+
  #scale_size_continuous(guide="none")+
  #add an equality line
  geom_abline(slope=1,intercept=0)+
  scale_y_continuous(limits=c(11,54))+
  scale_x_continuous(limits=c(11,54))

with_absorbed
```

The chart above entertains the idea of Warren dropping out and enthusiastically endorsing Sanders so effectively that all of her supporters switch to Sanders. Similar, it shows all Klobuchar and Buttigieg supporters in remaining states realigning to support Biden. This obviously won't happen in totality, but it gives us some idea of how a potential endorsement would change things. This looks slightly less bleak for Sanders. A handful of states shift above the line, but the gap does grow larger in other large states (notably Florida). 

To be clear, Warren hasn't dropped out yet and hasn't really indicated that she plans to. I won't comment on how many of her supporters are likely to support Sanders even if she does drop out and endorse him, but to have a chance, Sanders would need it to be **a lot**. 

As bleak as the picture is for Sanders, it's worth noting that we should be less confident in these current estimates than we were for Super Tuesday states. 

## Should we take these projections seriously? 

In a word, maybe? Even if we put aside the issue of potential realignment and just focus on the polling for Sanders and Biden, the answer isn't really clear.

Unfortunately, 538 doesn't seem to provide standard errors / margins of error / confidence intervals for their polling averages, but we can get some insight into their relative precision based on how often they've been polled.

On Super Tuesday, Sanders' actual vote share was extremely close to his polling averages in most contests. However, not every state is polled the same amount and not every poll is conducted by the same quality of pollsters. 

The early states were polled about as frequently as the upcoming contests relative to their delegate counts. However, 538 rates pollsters in terms of quality, and the upcoming contests have substantially fewer polls conducted by pollsters rated "B+" or better.

```{r compare_all_polls,echo=FALSE,message=FALSE,warning=FALSE}
#identify super tuesday states
super_tuesday_states<-delegate_table2%>%
  filter(grepl("Super",Date))%>%
  #create state by removing primary stuff
  mutate(state=gsub(" \\(.*?\\)","",Contest))%>%
  mutate(state=gsub(" party-run","",state))%>%
  mutate(state=gsub(" firehouse","",state))%>%
  mutate(state=gsub(" [A-z]*$","",state))%>%
  select(state)%>%unlist()
#add on Iowa, New Hampshire, Nevada, and SC
early_state<-c(super_tuesday_states,"Iowa","New Hampshire", "Nevada", "South Carolina")

#calculate number of polls for super tuesday vs non-super-tuesday states
#results in dataset with "variable" and "value" cols since that's what the donut function expects
all_polls<-primary_polls%>%
  #create indicator for whether or not state is early
  mutate(variable=ifelse(state%in%early_state,
                            "Super Tuesday or Earlier",
                            "Remaining States"))%>%
  group_by(variable)%>%
  summarise(value=n_distinct((poll_id)))%>%
  ungroup()%>%
  #create a variable indicating these are poll counts
  mutate(x="All polls")

#calculate the number of delegates remainining for after super tuesday
delegates_remaining<-delegate_table2%>%
  #remove total row
  filter(Contest!="Total")%>%
  #create state by removing primary stuff
  mutate(state=gsub(" \\(.*?\\)","",Contest))%>%
  mutate(state=gsub(" party-run","",state))%>%
  mutate(state=gsub(" firehouse","",state))%>%
  mutate(state=gsub(" [A-z]*$","",state))%>%
  #create variable indicating early vs later state
  mutate(variable=c(rep("Super Tuesday or Earlier",19),
                    rep("Remaining States",57-19)))%>%
  #make numeric pledge variable
  mutate(pledged=as.numeric(`State Pledged`))%>%
  group_by(variable)%>%
  summarise(value=sum(pledged))%>%
  ungroup()%>%
  #create a variable indicating these are Delegates
  mutate(x="Delegates")
quality_grades<-c("A+","A","A-","A/B","B+")
#quality polls 
quality_polls<-primary_polls%>%
  #limit only to quality polls
  filter(fte_grade%in%quality_grades)%>%
  #create indicator for whether or not state is early
  mutate(variable=ifelse(state%in%early_state,
                            "Super Tuesday or Earlier",
                            "Remaining States"))%>%
  group_by(variable)%>%
  summarise(value=n_distinct((poll_id)))%>%
  ungroup()%>%
  #create variable indicating these are for quality polls
  mutate(x="B+ or better polls")

rbind(all_polls,quality_polls,delegates_remaining)%>%
  #add a cumulative sum for labeling
  mutate(label_position = cumsum(value) - 0.5 * value) %>%
  ggplot(aes(x=x))+
  geom_bar(aes(y=value,fill=variable,label=comma(value)),
           stat="identity",position="fill",width=.4)+
  scale_fill_brewer(palette="Paired")+
  stat_identity(geom="text",
             aes(label=comma(value),
                 y=value,
                 group=variable),#group=variable),
             position=position_fill(vjust=0.5),
             color="white")+
  scale_y_continuous(label=percent)+
  labs(fill="",y="percentage",x="",
       title="Comparison of polls and delegates in finished vs upcoming contests")+
  theme_minimal()

```

While almost two-thirds of all pledged delegates are still up for grabs, fewer than half of all polls conducted by quality pollsters were conducted on remaining states. This may cast some doubt on the poll averages of future contests, which seem to show the race is Biden's to lose, but its difficult to quantify the extent.
